### 2010-12-01 report/report.tex
edited the team and acknowledgments

\section{Method}
% Describe in reasonable detail the algorithm you are using to address this 
% problem. A pseudo-code description of the algorithm you are using is 
% frequently useful. If it makes sense for your project, trace through a 
% concrete example, showing how your algorithm processes this example. The 
% example should be complex enough to illustrate all of the important aspects 
% of the problem but simple enough to be easily understood. If possible, 
% an intuitively meaningful example is better than one with meaningless 
% symbols.
We implemented and tested 8 different learning strategies:
\begin{itemize}
\item \emph{Uniform random hill climbing}: Creates a random neighbor by
  randomly choosing one parameter to adjust, and changing it completely 
  randomly in UniformStrategy(). Then evaluates this neighbor by running 
  the robot with the newly chosen parameters. If this neighbor results in a
  longer distance walked then the previous best neighbor, we save this
  neighbor as the new best neighbor. We then repeat the whole process
  using the best neighbor as a base.
\item \emph{Gaussian random hill climbing}: Creates a random neighbor by
  changing each parameter randomly based on a normal distribution. Then
  evaluates this neighbor similarly to uniform random hill climbing.
\item \emph{N-dimensional policy gradient descent}: Estimates the policy
  gradient by evaluating \emph{t} randomly generated policies
  near an initial parameter vector. Then computes the average score for
  each parameter and adjusts the base policy according to the estimated
  gradient.
\item \emph{Random}: Randomly generates policies in the range of the motion
representation.
\item \emph{Simplex (Nelder-Mead) Method}
\item \emph{Linear regression}: To initialize, chooses five random points
and trains on them using least-squares. Then in a loop, takes a fixed-size
step in the direction of the gradient, and retrains on all points so far.
\item \emph{SVM regression}
\item \emph{Evolutionary Neural Network (HYPERNEAT)\cite{2}}
\end{itemize}

@@

\section{Acknowledgments}
% List any people not on the team who helped you with your project: Your
% TA, other people you consulted with or had useful discussions (say in 
% a word or two what they did), people who proofread your report, and 
% any external code you used (libraries etc).

>>>>

\section{Method}
% Describe in reasonable detail the algorithm you are using to address this 
% problem. A pseudo-code description of the algorithm you are using is 
% frequently useful. If it makes sense for your project, trace through a 
% concrete example, showing how your algorithm processes this example. The 
% example should be complex enough to illustrate all of the important aspects 
% of the problem but simple enough to be easily understood. If possible, 
% an intuitively meaningful example is better than one with meaningless 
% symbols.
We implemented and tested 8 different learning strategies:
\begin{itemize}
\item \emph{Uniform random hill climbing}: Creates a random neighbor by
  randomly choosing one parameter to adjust, and changing it completely 
  randomly in UniformStrategy(). Then evaluates this neighbor by running 
  the robot with the newly chosen parameters. If this neighbor results in a
  longer distance walked then the previous best neighbor, we save this
  neighbor as the new best neighbor. We then repeat the whole process
  using the best neighbor as a base.
\item \emph{Gaussian random hill climbing}: Creates a random neighbor by
  changing each parameter randomly based on a normal distribution. Then
  evaluates this neighbor similarly to uniform random hill climbing.
\item \emph{N-dimensional policy gradient descent}: Estimates the policy
  gradient by evaluating \emph{t} randomly generated policies
  near an initial parameter vector. Then computes the average score for
  each parameter and adjusts the base policy according to the estimated
  gradient.
\item \emph{Random}: Randomly generates policies in the range of the motion
representation.
\item \emph{Simplex (Nelder-Mead) Method}
\item \emph{Linear regression}: To initialize, chooses five random points
and trains on them using least-squares. Then in a loop, takes a fixed-size
step in the direction of the gradient, and retrains on all points so far.
\item \emph{SVM regression}
\item \emph{Evolutionary Neural Network (HyperNEAT)\cite{2}}
\end{itemize}

@@

\section{Acknowledgments}
% List any people not on the team who helped you with your project: Your
% TA, other people you consulted with or had useful discussions (say in 
% a word or two what they did), people who proofread your report, and 
% any external code you used (libraries etc).
\begin{itemize}
\item Hod Lipson, Cornell Computational Synthesis Lab: advisor
\item Jim T\o rreson, University of Oslo: advisor
\item Juan Zagal, University of Chile: designed and printed robot and provided assistance
\item Jeff Clune, CCSL Red Couch: collaborated on HyperNEAT implementation/testing
\item Cooper Bills, Cornell University: assisted with Wii tracker development
\item Anshumali Srivastava, Cornell University: Teaching Assistant
\end{itemize}

\section{The Team}
% A table listing the names of the people who worked on the project, and who
% did what.
\begin{itemize}
\item Diana Hidalgo: 
\begin{itemize}
\item Simplex (Nelder-Mead)
\item \code{WiiTrackClient} and \code{WiiTrackServer} classes and hardware
\item Plotting and evaluating results
\end{itemize}
\item Sarah Nguyen
\begin{itemize}
\item Random
\item Uniform random hill climbing
\item Gaussian random hill climbing
\item N-dimensional policy gradient descent
\item Linear regression and prediction
\item \code{RunManager} and \code{Strategy} classes
\item Video editing
\end{itemize}
\item Jason Yosinski
\begin{itemize}
\item SVM regression and prediction
\item Evolutionary Neural Network (HyperNEAT)
\item \code{WiiTrackClient} and \code{WiiTrackServer} classes and hardware
\item \code{Robot}, \code{RunManager}, and \code{Strategy} classes
\item \code{Parameterized Motion Model} abstract base class
\item \code{SineModel} classes
\item \code{explore\_dimensions}
\item Plotting and evaluating results
\end{itemize}
\end{itemize}
